Identifying Departures from the Fully Developed Speckle Hypothesis in Intensity SAR Data with Non-Parametric Estimation of the Entropy

### 2024-01-19 Text/Articles/MIGARS_2024/R1-The Entropy as a Proxy for Fully Developed Speckle.Rmd
simulation test with Real SAR Images

header-includes:
   - \usepackage[english]{babel}
   - \usepackage{bm,bbm}
   - \usepackage{mathrsfs}
   - \usepackage{siunitx}
   - \usepackage{graphicx}
   - \usepackage{url}
   - \usepackage[T1]{fontenc}
   - \usepackage{polski}
   - \usepackage{booktabs}
   - \usepackage{color}
   - \usepackage{mathtools}
   - \usepackage[utf8]{inputenc}
   - \usepackage{hyperref}
   - \hypersetup{draft}
   - \usepackage{graphicx}
   - \usepackage{float}
   - \usepackage{booktabs}
   - \usepackage{array}
   - \usepackage{multirow}
   - \usepackage{wrapfig}
   - \usepackage{colortbl}
   - \usepackage{pdflscape}
   - \usepackage{xcolor}
   - \usepackage{amsmath}
   - \usepackage{mathabx}
  # - \usepackage{pgf}
   - "\\setcitestyle{square,comma,numbers,sort&compress}" # citation style to numerical, work with \cite{} or [@]

output:
  rticles::ieee_article:
    number_sections: TRUE
    citation_package: natbib

@@

@@

source("../../../Code/R/MainFunctions/bootstrap_van_es_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_correa_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_ebrahimi_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_noughabi_arghami_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_vasicek_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_al_omari_1_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_al_omari_2_estimator.R")
#The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
source("../../../Code/R/Programs/functions_sample_bias_mse.R")#

@@

R <- 500
mu <- 1
B <- 2
alpha1 <- -8
sample.size <- c(50, 100, 150, 200, 250,300, 350)
L_values <- c(2, 5, 8, 18)

@@

# table
table_result_combined <- kbl(
  combined_summary_stats,
  caption = "Descriptive analysis of $S(Z)$ for different values of $L$, and $\\mu=1$.",
  format = "latex",
  booktabs = TRUE,
  align = "c",
  escape = FALSE,
  digits = 4,
  label = "table_stat_combined"
) %>%
  collapse_rows(latex_hline = "major", valign = "middle")# %>%
 # kable_styling(latex_options = c("striped", "hold_position"), full_width = FALSE)

@@

>>>>

header-includes:
   - \usepackage[english]{babel}
   - \usepackage{bm,bbm}
   - \usepackage{mathrsfs}
   - \usepackage{siunitx}
   - \usepackage{graphicx}
   - \usepackage{url}
   - \usepackage[T1]{fontenc}
   - \usepackage{polski}
   - \usepackage{booktabs}
   - \usepackage{color}
   - \usepackage{mathtools}
   - \usepackage[utf8]{inputenc}
   - \usepackage{hyperref}
   - \hypersetup{draft}
   - \usepackage{graphicx}
   - \usepackage{float}
   - \usepackage{booktabs}
   - \usepackage{array}
   - \usepackage{multirow}
   - \usepackage{wrapfig}
   - \usepackage{colortbl}
   - \usepackage{pdflscape}
   - \usepackage{xcolor}
   - \usepackage{amsmath}
   - \usepackage{mathabx}
   - \usepackage{subfig}
   #- \usepackage{subcaption}
  # - \usepackage{pgf}
   - "\\setcitestyle{square,comma,numbers,sort&compress}" # citation style to numerical, work with \cite{} or [@]

output:
  rticles::ieee_article:
    number_sections: TRUE
    citation_package: natbib
    #extra_dependencies: "subfig"
    #keep_tex: yes

@@

#library(grid)

@@

source("../../../Code/R/MainFunctions/bootstrap_van_es_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_correa_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_ebrahimi_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_noughabi_arghami_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_vasicek_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_al_omari_1_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_al_omari_2_estimator.R")
#The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
source("../../../Code/R/Programs/functions_sample_bias_mse.R")# read_ENVI_images
source("../../../Code/R/Programs/read_ENVI_images.R")

@@

R <- 1000
mu <- 1
B <- 2
alpha1 <- -8
sample.size <- c(50, 100, 150, 200, 250,300, 350)
L_values <- c(2, 5, 8, 18)

@@

# table
table_result_combined <- kbl(
  combined_summary_stats,
  caption = "Descriptive analysis of $S(Z)$ for different values of $L$, and $\\mu=1$.",
  format = "latex",
  booktabs = TRUE,
  align = "c",
  escape = FALSE,
  digits = 4,
  label = "table_stat_combined"
) %>%
  collapse_rows(latex_hline = "major", valign = "middle") %>%
   kable_styling(latex_options = "scale_down")
 # kable_styling(latex_options = c("striped", "hold_position"), full_width = FALSE)

@@

## Real SAR Images

```{r Real_SAR_Images, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.cap='Real SAR images', fig.subcap=c('Amazonas', 'Flevoland','Ottawa', 'Berlin' ), out.width='.48\\linewidth',  fig.ncol=2}
knitr::include_graphics("../../../Figures/PNG/Brazil_Intensity_VV.png")
#knitr::include_graphics("../../../Figures/PNG/Berlin_Intensity_VV.png")

knitr::include_graphics("../../../Figures/PNG/Flevoland_Intensity_VV.png")
knitr::include_graphics("../../../Figures/PNG/Ottawa_Intensity_VV.png")
knitr::include_graphics("../../../Figures/PNG/BER_Intensity_VV.jpg")
```

```{r SAR_simulations, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#, cache = TRUE, autodep = TRUE
set.seed(1234567890, kind = "Mersenne-Twister")
x_Brazil <- myread.ENVI(file='../../../Data/SAR/Brazil/Intensity_VV.img', headerfile='../../../Data/SAR/Brazil/Intensity_VV.hdr')
x_Berlin<- myread.ENVI(file='../../../Data/SAR/Berlin/Intensity_VV.img', headerfile='../../../Data/SAR/Berlin/Intensity_VV.hdr')
x_Flevoland <- myread.ENVI(file='../../../Data/SAR/Flevoland/Intensity_VV.img', headerfile='../../../Data/SAR/Flevoland/Intensity_VV.hdr')
x_Ottawa <- myread.ENVI(file='../../../Data/SAR/Ottawa/Intensity_VV.img', headerfile='../../../Data/SAR/Ottawa/Intensity_VV.hdr')

#Brazil
nRows_Brazil <- 518
nCols_Brazil <- 519

centerRow_Brazil <- floor(nRows_Brazil / 2)
centerCol_Brazil <- floor(nCols_Brazil / 2)

roiSize_Brazil <- 200

# 
roiStartRow_Brazil <- centerRow_Brazil - floor(roiSize_Brazil / 2) + 1
roiEndRow_Brazil <- roiStartRow_Brazil + roiSize_Brazil - 1

roiStartCol_Brazil <- centerCol_Brazil - floor(roiSize_Brazil / 2) + 1
roiEndCol_Brazil <- roiStartCol_Brazil + roiSize_Brazil - 1

# Extraer el ROI
roi_Brazil <- x_Brazil[roiStartRow_Brazil:roiEndRow_Brazil, roiStartCol_Brazil:roiEndCol_Brazil]

mean_data_brasil <- mean(roi_Brazil)
Entropy_brasil <- correa_estimator(roi_Brazil)
entropia_estimada_boot_brasil <- bootstrap_correa_estimator( roi_Brazil, 10)
True_entropy_brasil <-(log(mean( roi_Brazil)) + (5 - log(5) + lgamma(5) + (1 - 5) * digamma(5)))
Test_difference_brasil <- bootstrap_correa_estimator_log_mean( roi_Brazil, 10)- ( (5 - log(5) + lgamma(5) + (1 - 5) * digamma(5)))
#difference_correa_brasil <- correa_estimator( roi_Brazil) - log(mean(roi_Brazil))- ( (5 - log(5) + lgamma(5) + (1 - 5) * digamma(5)))

#Berlin
nCols_Berlin  = 501
nRows_Berlin  = 501

centerRow_Berlin <- floor(nRows_Berlin / 2)
centerCol_Berlin <- floor(nCols_Berlin / 2)

roiSize_Berlin <- 200

# Calcular las coordenadas del ROI
roiStartRow_Berlin <- centerRow_Berlin - floor(roiSize_Berlin / 2) + 1
roiEndRow_Berlin <- roiStartRow_Berlin + roiSize_Berlin - 1

roiStartCol_Berlin <- centerCol_Berlin - floor(roiSize_Berlin / 2) + 1
roiEndCol_Berlin <- roiStartCol_Berlin + roiSize_Berlin - 1

# Extraer el ROI
roi_Berlin<- x_Berlin[roiStartRow_Berlin:roiEndRow_Berlin, roiStartCol_Berlin:roiEndCol_Berlin]

mean_data_Berlin <- mean(roi_Berlin)
Entropy_Berlin <- correa_estimator(roi_Berlin)
entropia_estimada_boot_Berlin <- bootstrap_correa_estimator( roi_Berlin, 10)
True_entropy_Berlin <-(log(mean( roi_Berlin)) + (5 - log(5) + lgamma(5) + (1 - 5) * digamma(5)))
Test_difference_Berlin <- bootstrap_correa_estimator_log_mean( roi_Berlin, 10)- ( (5 - log(5) + lgamma(5) + (1 - 5) * digamma(5)))
#difference_correa_Berlin <- correa_estimator( roi_Berlin) - log(mean(roi_Berlin))- ( (5 - log(5) + lgamma(5) + (1 - 5) * digamma(5)))

# Flevoland
nCols_Flevoland = 355
nRows_Flevoland = 354

centerRow_Flevoland <- floor(nRows_Flevoland / 2)
centerCol_Flevoland <- floor(nCols_Flevoland / 2)

roiSize_Flevoland <- 200

#  coordenadas del ROI
roiStartRow_Flevoland <- centerRow_Flevoland - floor(roiSize_Flevoland / 2) + 1
roiEndRow_Flevoland <- roiStartRow_Flevoland + roiSize_Flevoland - 1

roiStartCol_Flevoland <- centerCol_Flevoland - floor(roiSize_Flevoland / 2) + 1
roiEndCol_Flevoland <- roiStartCol_Flevoland + roiSize_Flevoland - 1

# Extraer el ROI
roi_Flevoland<- x_Flevoland[roiStartRow_Flevoland:roiEndRow_Flevoland, roiStartCol_Flevoland:roiEndCol_Flevoland]

mean_data_Flevoland <- mean(roi_Flevoland)
Entropy_Flevoland <- correa_estimator(roi_Flevoland)
entropia_estimada_boot_Flevoland <- bootstrap_correa_estimator( roi_Berlin, 10)
True_entropy_Flevoland <-(log(mean( roi_Flevoland)) + (5 - log(5) + lgamma(5) + (1 - 5) * digamma(5)))
Test_difference_Flevoland <- bootstrap_correa_estimator_log_mean( roi_Flevoland, 10)- ( (5 - log(5) + lgamma(5) + (1 - 5) * digamma(5)))
#difference_correa_Flevoland <- correa_estimator( roi_Flevoland) - log(mean(roi_Flevoland))- ( (5 - log(5) + lgamma(5) + (1 - 5) * digamma(5)))

#----------------------------------------------
#ottawa
nCols_Ottawa = 572
nRows_Ottawa= 558

centerRow_Ottawa  <- floor(nRows_Ottawa / 2)
centerCol_Ottawa  <- floor(nCols_Ottawa  / 2)

 roiSize_Ottawa <- 100
# 
# # Coordenadas del ROI en la parte superior
 roiUpperStartRow <- 1
 roiUpperEndRow <- roiUpperStartRow + roiSize_Ottawa - 1
# 
 roiUpperStartCol <- centerCol_Ottawa - floor(roiSize_Ottawa / 2) + 1
 roiUpperEndCol <- roiUpperStartCol + roiSize_Ottawa - 1
# 
# # Extraer el ROI en la parte superior
 roi_Ottawa<- x_Ottawa[roiUpperStartRow:roiUpperEndRow, roiUpperStartCol:roiUpperEndCol]

 mean_data_Ottawa <- mean(roi_Ottawa)
 Entropy_Ottawa <- correa_estimator(roi_Ottawa)
 entropia_estimada_boot_Ottawa <- bootstrap_correa_estimator( roi_Ottawa, 10)
 True_entropy_Ottawa <-(log(mean( roi_Ottawa)) + (5 - log(5) + lgamma(5) + (1 - 5) * digamma(5)))
 Test_difference_Ottawa <- bootstrap_correa_estimator_log_mean( roi_Ottawa, 10)- ( (5 - log(5) + lgamma(5) + (1 - 5) * digamma(5)))
 #difference_correa_Ottawa <- correa_estimator( roi_Ottawa) - log(mean(roi_Ottawa))- ( (5 - log(5) + lgamma(5) + (1 - 5) * digamma(5)))

 resultados_df <- data.frame(
   Ciudad = c("Amazonas", "Berlin", "Flevoland", "Ottawa"),
   Media = c(mean_data_brasil, mean_data_Berlin, mean_data_Flevoland, mean_data_Ottawa),
   Entropia_Estimada = c(Entropy_brasil, Entropy_Berlin, Entropy_Flevoland, Entropy_Ottawa),
   Entropia_Estimada_Boot = c(entropia_estimada_boot_brasil, entropia_estimada_boot_Berlin, entropia_estimada_boot_Flevoland, entropia_estimada_boot_Ottawa),
   Entropia_Verdadera = c(True_entropy_brasil, True_entropy_Berlin, True_entropy_Flevoland, True_entropy_Ottawa),
   Diferencia_Test_Entropia = c(Test_difference_brasil, Test_difference_Berlin, Test_difference_Flevoland, Test_difference_Ottawa)

 )

 colnames(resultados_df) <- c("Area", "mean", "$\\widehat{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{C}}$", "$H_{\\Gamma_{\\text{SAR}}}$", "$S(Z)$")

#
print(
  kbl(
    resultados_df,
    caption = "Results of applying the statistical test to SAR images.",
    format = "latex",
    booktabs = TRUE,
    align = "c",
    escape = FALSE, 
    digits = 4,  
    label = "table_sar", 
  ) %>%
    collapse_rows( latex_hline = "major", valign = "middle")
)
```
